---
title: "Regression Template"
author: "Author 1, Author 2, Author 3"
institute: "Appalachian State Univeristy"
date: last-modified
date-format: "MMMM DD, YYYY"
format:
  revealjs:
    theme: sky
editor: visual
bibliography: citations.bib
---

## Data Set and Background

The data set used for this presentation is [Communities and Crime Unnormalized](https://archive.ics.uci.edu/dataset/211/communities+and+crime+unnormalized) contributed by @misc_communities_and_crime_unnormalized_211


```{r, echo = FALSE}
library(data.table)
comm_crime <- fread("./DATA/CommViolPredUnnormalizedData.txt")
# Note the columns are not labelled....must dig out information 
COL_NAMES <- c("community_name", "state", "county_code", "community_code", "fold","population", "householdsize",
               "racepctblack", "racepctwhite", "racepctasian", "racepcthisp", "agepct12t21", "agepct12t29", "agepct16t24", "agepct65up",
               "numburban", "pcturban", "medincome", "pctwwage", "pctwfarmself",
               "pctwinvinc", "pctwsocsec", "pctwpubasst", "pctwretire", "medfaminc",
               "percapinc", "whitepercap", "blackpercap", "indianpercap", "asianpercap",
               "otherpercap", "hisppercap", "numunderpov", "pctunderpov", "pctless9thgrade", "pctnothsgrad", "pctbsormore", "pctunemployed", "pctemploy", "pctmanemploy", "pctemplprofserv", "pctoccupmanu", "pctoccupmgmtprof", "malepctdivorce",
               "malepctnevmarr", "femalepctdiv", "totalpctdiv", "persperfam", "pctfam2par", "pctkids2par", "pctyoungkids2par", "pctteen2par", "pctworkmomyoungkids",
               "pctworkmom", "numkidsbornnevenmar", "pctkidsbornnevermar", "num_immig","pct_immig_recent", "pct_immig_rec5", "pct_immig_rec8", "pct_immig_rec10",
               "pct_recent_immig", "pct_rec_immig5", "pct_rec_immig8", "pct_rec_immig10", "pct_speak_eng_only", "pct_not_speak_engl_well", "pct_large_house_fam", "pct_large_house_occup", "pers_per_occup_house",
               "pers_per_own_occup_house", "pers_per_rent_occup_house",
               "pct_pers_own_occup", "pct_pers_dense_house", "pct_house_less3br",
               "median_num_br", "house_vacant", "pct_house_occup", "pct_house_own_occup", "pct_vacant_boarded", "pct_vacant_more6mos",
               "med_year_house_built", "pct_house_no_phone", "pct_wo_full_plumb",
               "own_occup_low_quart", "own_occup_median", "own_occup_hi_quart", "own_occ_range", "rent_q1", "rent_q2", "rent_q3", "rent_range", "med_rent", "med_rent_pct_house_inc", "med_own_cost_inc", "med_own_cost_pct_inc", "med_own_cost_pct_inc_no_mtg", "num_in_shelters", "num_in_street", "pct_foreign_born",
               "pct_born_same_state", "pct_same_house85", "pct_same_city85", "pct_same_state85", "lemas_sworn_ft", "lemas_sw_ft_per_pop", "lemas_sw_ft_field_ops", "lemas_sw_ft_field_per_pop", "lemas_total_req", "lemas_total_req_per_pop", "police_req_per_offic", "police_per_pop", "racial_match_comm_pol", "pct_police_white",
               "pct_police_black", "pct_police_hisp", "pct_police_asian", "pct_police_minor", "office_assign_drug_units", "num_kinds_drugs_seized",
               "police_avg_ot_worked", "land_area", "pop_dens", "pct_use_pub_trans",
               "poice_cars", "police_oper_budg", "lemas_pct_police_on_ptrl", "lemas_gang_unit_deploy", "lemas_pct_officer_drug", "police_budg_per_pop", "murders_in_1995", "murders_per_pop", "rapes_in_1995", "rapes_per_pop", "robberies_in_1995", "robberies_per_pop", "assaults_in_1995", "assualts_per_pop", "burglaries_in_1995", "burglaries_per_pop", "larcenies_in_1995", "larcenies_per_pop", "auto_theft_in_1995", "auto_theft_per_pop", "arsons_in_1995", "arsons_per_pop", "violent_crimes_per_pop", "non_violent_crimes_per_pop")
```



## Bullets

When you click the **Render** button a document will be generated that includes:

-   Content authored with markdown
-   Output from executable code

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

## References
